Explainable Functional Region Identification

### 2018-11-25 paper.tex
abstractconclusion

\begin{abstract}
Functional region identification is a critical step towards Urban computing.
The state-of-the-art Dirichlet Multinomial Regression(DMR) has identify regions with different function based on topic cluster modeling.
Due to the ingenious structure inside the complex model, its result is beyond the direct comprehension of humans.
How to give them reliable explanations are the main objectives of this work.
To improve the persuasiveness of its result, we proposed a post hoc framework to make explanation for it.
Optimal latent factor model was applied as explanation after the identification.
We use matrix factorization to get latent factors and correlate latent factors with urban feature.
The selected urban feature can be labeled as the explanation.
Our framework can give an strong evidence to the identification and enhance the satisfaction of users and system designers.

(15--250 words.)

@@

%contribution
Contribution of this work is three-fold. (1) \textbf{An Unexplored Problem.} To the best of our knowledge, we are the first to study the problem of explainable functional region identification. (2) \textbf{A New Form of Explanations.} We propose a novel framework to deliver explanations. The proposed EFRI explains the functional of a region by demonstrating both the semantics of functional (through urban activities and urban features) and mobility patterns of the functional (time sensitive mobility patterns). Such informative explanations can greatly improve user experience and might shed some insights in other domains such as explainable recommendations. (3) \textbf{A Novel Model.} We present a unsupervised framework to extract urban activities and urban features from online review data. We then adopt a layered regression model to semanticaly associate regions to urban features. We also embed a free-form bias curve to represent mobility pattrerns in mobility data.

@@

\section{Conclusion}\label{sec:conclusions}
Function regions identification is an important part of urban computing.
But its evaluation depend on human intuition and urban planning, which is hard to display in terms of statistics.
To make up for the lack of persuasive explanation, we proposed a post hoc framework to give persuasive explanation for functional regions identification in this paper.
Our datasets including over 3 million comments of shops and taxicabs OD pair trajectory in November 2016 generated by more than 7 million orders.
We utilized the framework to general most relative labels for every single region units as explanation.
According to the experiments performed in the datasets, our framework give an strong evidence to the identification and enhance its persuasiveness.
The result can help users and urban system designers easily recognize the region functions, which is helpful in a variety of urban applications, such as urban planning, location choosing for a business advertisement casting, and so on.

There are some directions can improve in the future work.
First is to full utilize our data sets of trajectory. 
Our trajectory datasets not only have origin and destination, but also include the detail points that users have passed by.
There are also some interesting patterns within these process points, and we can find new moving patterns in it. 
Second, we want to change our phrase-level explanation into sentence-level, which is more similar to natural language.

>>>>

\begin{abstract}
As a critical step in urban computing, functional region identification (FRI) has attracted a lot of research attention.
Existing research generally cluster city regions based on human mobility data where the cluster labels are difficult to interpret.
In this paper, we explore the problem of explainable functional region identification (EFRI), which integrates online geo-tagged textual data and mobility data to deliver explanations of any FRI results. 
We  explain a region's function through a set of urban activities and urban features, which are automatically extracted from online textual data.
We  build a layered regression model to to infer each region's relevance to urban features. The diverse and time-sensitive mobility patterns are encoded in a free-form bias curve in the regression model.
We conduct comprehensive experiments to verify the accuracy of extracted urban features and the interpretability of the proposed EFRI system.

@@

%contribution
Contribution of this work is three-fold. (1) \textbf{An Unexplored Problem.} To the best of our knowledge, we are the first to study the problem of explainable functional region identification. (2) \textbf{A New Form of Explanations.} We propose a novel framework to deliver explanations. The proposed EFRI explains the functional of a region by demonstrating both the semantics of functional (through urban activities and urban features) and mobility patterns of the functional (time sensitive mobility patterns). Such informative explanations can greatly improve user experience and might shed some insights in other domains such as explainable recommendations. (3) \textbf{A Novel Model.} We present a unsupervised framework to extract urban activities and urban features from online review data. We then adopt a layered regression model to semantically associate regions to urban features. We also embed a free-form bias curve to represent mobility pattrerns in mobility data.

@@

\section{Conclusion}\label{sec:conclusions}
We present a novel explainable functional region identification (EFRI) system.
We provide post-hoc explanations which describe the results of any FRI system through a set of urban activities and urban features automatically extracted from online textual data.
We further embed the diverse and time-sensitive mobility patterns revealed in mobility data with semantic associations in textual data.
Experiments show that our system can extracted high quality urban features and provide reasonable explanations.

In future work we will explore more information sources such as tweets and news reports to incorporate the power of big data in EFRI.
With massive amounts of textual data that covers all areas of urban lives, more human activities can be explained.
Another future direction is to adopt new styles of explanations. 
For example, explanations in nature language are more friendly to end-users.
Visualizing the explanations is beneficial for government officers and system designers.
